%-------------------------
% Resume in Latex
% Author : Avinash Kumar Jha
% Based off of: https://github.com/abhishekarya1/resume-latex
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{setspace}
\setlength{\parskip}{0.5em}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\input{glyphtounicode}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\linespread{1.05}
\setlength{\itemsep}{0.2em}

\titleformat{\section}{\vspace{-8pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\fontsize{8.6}{10.32}\selectfont{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & {\fontsize{10}{12}\selectfont #2} \\\vspace{2pt}\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1.2em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\fontsize{24}{28.8}\selectfont \scshape Avinash Kumar Jha} \\ \vspace{8pt}
    \fontsize{10}{12}{\selectfont
    \href{tel:+91-9811525897}{\underline{+91-9811525897}} \hspace{0.5em}$|$\hspace{0.5em}
    \href{mailto:avinash2002a@gmail.com}{\underline{avinash2002a@gmail.com}} \hspace{0.5em}$|$\hspace{0.5em} 
    \href{https://avinashjha.space}{\underline{avinashjha.space}} \hspace{0.5em}$|$\hspace{0.5em}
    \href{https://www.linkedin.com/in/avikrjha}{\underline{linkedin.com/in/avikrjha}}
    }
\end{center}

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Full Stack Engineer}{Mar 2025 -- Present}{thinkinteraction.in}{Remote}
\resumeItemListStart
\resumeItem{Designed and implemented a microfrontend architecture using RequireJS, React, and Vite, enabling modular applications with cross-widget drag-and-drop, notifications, and inter-widget communication.}
\resumeItem{Built scalable APIs with NestJS + TypeScript, integrating automated tests to prevent regressions and improve production reliability.}
\resumeItem{Delivered a high-performance Remix frontend (SSR + CSR), improving TTFB, SEO, and reducing redundant re-renders via optimized caching and state management.}
\resumeItem{Introduced a monorepo with shared logic packages, streamlining development and accelerating feature rollout.}
\resumeItem{Automated GCP VM deployments using Bash, Docker, and SSH, cutting manual deployment time by 60\% and reducing costs by 20\%.}
\resumeItem{Designed and implemented CI/CD pipelines using GitHub Actions, enabling automated build, test, and deployment workflows across services.}
\resumeItem{Developed a natural language search system, enabling users to query data using free-form text and improving search relevance and usability.}
\resumeItemListEnd

\resumeSubheading{Full Stack Engineer}{Jan 2024 -- Mar 2025}{Stackkaroo}{Remote}
\resumeItemListStart
\resumeItem{Developed full-stack projects across diverse tech stacks (Next.js, MERN, Django-React, Flask-Jinja, PHP) adapting quickly to client requirements.}
\resumeItem{Built a WebGI-based 3D jewelry configurator boosting engagement and conversions.}
\resumeItem{Created a JS-based Fixed Deposit calculator to compare RBI rates, improving user decision-making.}
\resumeItem{Reviewed code, coordinated with other developers, and enforced code quality standards.}
\resumeItem{Built interactive 3D room tours using React Three Fiber, Drei, and Three.js for real estate and interior design clients.}
\resumeItemListEnd

\resumeSubheading{Frontend Developer (Intern)}{Aug 2023 -- Jan 2024}{Stackkaroo}{Remote}
\resumeItemListStart
\resumeItem{Built a custom static website for a bank foundation with GSAP animations.}
\resumeItem{Integrated Strapi and Concrete CMS to streamline content workflows.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Dr. Akhilesh Das Gupta Institute of Technology}{2022 -- 2026}{Bachelor of Technology (B.Tech), Information Technology}{Delhi, India}
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{\textbf{Programming:} JavaScript, TypeScript, Python, Bash, C, C++, GLSL \\
\textbf{Frameworks:} Next.js, NestJS, Remix.js, Redux.js, Three.js, TypeORM, Mongoose, Prisma, Vite, FastAPI, Flask, Django \\
\textbf{Tools:} Git, Docker, Linux, GCP, AWS, GitHub Actions, MySQL, MongoDB, PostgreSQL \\
\textbf{AI:} Claude code, MCP, Acli}
\end{itemize}

\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{NAS System in C} | Network Storage Server}
{\href{https://github.com/avisord/chttp2}{\underline{GitHub}}}
\resumeItemListStart
\resumeItem{A lightweight Network Attached Storage (NAS) system in C for managing and accessing files over a web interface.}
\resumeItem{Developed a custom backend server to handle file uploads, downloads, and real-time content preview in the browser.}
\resumeItem{Designed the system to support multiple users with secure access and isolated file handling.}
\resumeItem{Structured the application with a modular design, allowing easy extension with new features and integrations.}
\resumeItem{Optimized performance for efficient file handling and smooth user experience during large file transfers.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Imaginary Storage} | Cloud Storage Platform}{\href{https://github.com/Jhaempyre/imaginestorage}{\underline{GitHub}}}
\resumeItemListStart
\resumeItem{Designed and built a provider-agnostic cloud storage platform where users have full control over file upload, preview, sharing, and deletion.}
\resumeItem{Integrated AWS and GCP options for storage backends, giving users flexibility and cost efficiency.}
\resumeItem{Developed a highly interactive and responsive web UI to deliver a smooth user experience.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{MeloSynthiaAI} | AI-powered Music Composition (Hackathon Award Winner)}{\href{https://github.com/AYUSHMAN0503/MeloSynthiaAI}{\underline{GitHub}}}
\resumeItemListStart
\resumeItem{Built an ML-driven system capable of generating music based on genre, instruments, and user prompts.}
\resumeItem{Created a pipeline to package and sell generated tracks as digital artifacts, demonstrating real-world product potential.}
\resumeItemListEnd

\resumeSubHeadingListEnd


\end{document}
